A linear inside-outside algorithm for detecting next generation sequencing errors in structured RNAs

### 2012-10-07 Recomb/results_RECOMB.tex
new roc figs
time

To evaluate our method, we computed a ROC curve representing the performance of a classifier based on the mutational probabilities computed by
\RNApyro. We reported in Table \ref{tab:benchmark} the area under the curve (AUC). More specifically, we fix a threshold $\lambda \in [0,1]$ and we
predict an error at position $i$ in sequence $\omega$ if and only if the probability $P(i,n)$ of a nucleotide $n \in \{ A,C,G,U \}$ exceed this threshold.
The set of corrections is thus $\{ n \; | \;  n \in \{ A,C,G,U \} \mbox{ and } P(i,n) > \lambda \mbox{ and }  n \neq \omega[i] \}$, where $\omega[i]$ is the
nucleotide at position $i$ in the input sequence. Then, we progressively vary $\lambda$ between $0$ and $1$ to calculate the ROC curve and the AUC.

\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
& 1.0 & 0.5 & 0. \\
\hline
6 & 0.69 & 0.72 & 0.74 \\
12 & 0.80 & 0.84 & 0.84 \\
24 & 0.76 & & \\
\hline
\end{tabular}
\end{center}
\caption{Performance of error-correction. The row index indicates the number of mutations performed with \RNApyro, and the column index indicates
the value of the parameter $\alpha$ distributing the weights of stacking pair energies vs isostericity scores. In each cell, we report the average AUC
values over the 10 experiments.}
\label{tab:benchmark}
\end{table}

>>>>

To evaluate our method, we computed a ROC curve representing the performance of a classifier based on the mutational probabilities computed by
\RNApyro. We report in Table \ref{tab:benchmark} the area under the curve (AUC). More specifically, we fix a threshold $\lambda \in [0,1]$ and we
predict an error at position $i$ in sequence $\omega$ if and only if the probability $P(i,n)$ of a nucleotide $n \in \{ A,C,G,U \}$ exceed this threshold.
The set of corrections is thus $\{ n \; | \;  n \in \{ A,C,G,U \} \mbox{ and } P(i,n) > \lambda \mbox{ and }  n \neq \omega[i] \}$, where $\omega[i]$ is the
nucleotide at position $i$ in the input sequence. Then, we progressively vary $\lambda$ between $0$ and $1$ to calculate the ROC curve and the AUC.

\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
& 1.0 & 0.5 & 0. \\
\hline
6 & 0.69 & 0.72 & 0.74 \\
12 & 0.80 & 0.84 & 0.84 \\
24 & 0.76 & 0.84 & 0.84 \\
\hline
\end{tabular}
\end{center}
\caption{Performance of error-correction. The row index indicates the number of mutations performed with \RNApyro, and the column index indicates
the value of the parameter $\alpha$ distributing the weights of stacking pair energies vs isostericity scores. In each cell, we report the average AUC
values over the 10 experiments.}
\label{tab:benchmark}
\end{table}

\begin{figure}
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics[width=1.2\textwidth]{figures/ROC_6.pdf}
\caption{6 mutations}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics[width=1.2\textwidth]{figures/ROC_12.pdf}
\caption{12 mutations}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics[width=1.2\textwidth]{figures/ROC_24.pdf}
\caption{24 mutations}
\end{subfigure}
\end{figure}

\subsection{Time}
The applications for this algorithms implies a need for efficiency
and scalability. In Table~\ref{tab:time} we
present different times needed to compute the probabilities for
 every nucleotide at every positions for a vast set of parameters.

\begin{table}
\begin{center}
\begin{tabular}{llccc}
$|s|$&$|\Omega|$&\multicolumn{3}{c}{Number of mutations}\\\cline{3-5}
		 & 				  & 6   &  12  & 24\\\cline{3-5}
100  & 44				& 35s  & 238s & 1023s\\
300  & 44				& 135s & 594s &2460s\\

\end{tabular}
\end{center}
\caption{Time to compute all probabilities. The first column indicates the length, the second
 the size of $\Omega$ and  the column indexes indicate the number
 of mutations. $\alpha$ is
set at $0.5$, and $\beta=1.5$ and All sequences are generated randomly.}
\label{tab:time}
\end{table}
